\LARGE \bf Laser Tracker Placement Optimization for highly flexible manufacturing systems

### 2024-08-04 paper/paper.tex
polished state of the art

\section{Introduction}

\section{State of the art}

>>>>

\section*{Abstract}
In recent years, modular and reconfigurable manufacturing systems have gained attention for their adaptability. 
While system design is now highly automated, designing the verification setup remains a manual design problem involving tasks like placing external sensors to measure performance. 
This paper argues that design optimization approaches for manufacturing systems can also automate the design of the verification setup.
This is demonstrated using the placement of a laser tracker system with markers that due to their line-of-sight complexity and simultaneous measurement of multiple systems can be challenging to design.
We present a straightforward optimization approach to demonstrate potential automation in this area.
\section{Introduction}

\section{State of the art}
The work presented in this paper intersects two research fields: manufacturing systems optimization and sensor placement optimization. 
Our primary question is what aspects of a manufacturing system we need to verify. 
We focus on system-based verification rather than product-based, aiming to measure the performance of the manufacturing system, not the resulting product quality.
In particular we focuss on approaches that solves what~\cite{reconfigurable_production} calls reconfiguration design problem.
This involves either combining fixed modules to form a system or directly optimizing the sytems physical design.
 Examples include robot cell optimization problems~\cite{previous_work, stiffness_placement} and robot design optimization problems~\cite{task_synthesis, ad-hoc_manipulator, multi_objective}. 
 For a manufacturing perspective, works such as~\cite{johannes_1, johannes_2} are relevant.
 All of these approaches focus on phyiscal capabilities such as payload, accuracy, stiffness, force, weight, and motion.

To verify that the optimized system configuration achieves the desired performance, we need to measure the system's performance using external sensors, 
however in all of the above works the sensor placement for verification (if done at all) is done manually.
This can be a challening task which brings us to the field of sensor placement optimization.
The goal here is to find the optimal sensor placement for accurate system performance measurement.
A adjecent engineering discipline in which sensor placement optimization is a already well studied is structural health monitoring~\cite{shms}.
Here key algorithms where already identified such as genetic algorithms, particle swarm optimization, and simulated annealing~\cite{shms}.
Based on these works we will also use a particle swarm optimization algorithm for our problem.
However the field of structural health monitoring mainly considers static systems while our manufacturing systems are by nature dynamic.
This introduces additional challenges since the sensor placement needs to account for the systems total trajectory.
This challenge has only recently been addressed in manufacturing systems~\cite{ieee_sensors}. Although this early work focuses on process control, not system verification, its methodologies are applicable, 
emphasizing optimizing an objective integrated over total process time. 
However, since we are not using cameras as in the previous study, we must derive our own visibility model reflecting the measurement characteristics of a laser tracker.
This will be the focus of the next section.
